Model Trials

### 2018-01-31 Models.Rmd
update 1/31

## Basic lm to assess predictors of interest
-site-level predictors: scar.BM, scar.DEN, benthic (PC1,PC2) (excluding carn.BM because almost fully cor. with scar.BM)
-fish-level predictors: species, phase, length
--eventually run separately for different species
--species*scar.BM interaction?
-response variables: g.frac, BR (?), and FR (run separately) *should I calculate site means at this point a la Nash et al?

### Feeding rates
```{r}
lm_FR <- lm(FR~scar.BM*Species+Phase+Length.cm+PC1+PC2, data=data)
summary(lm_FR)
```
*Notes: nearly everything is significant? Significant interaction between scar.BM and species for Spar. viride.*
*R2 goes up slightly with initial only*

### Fraction of time grazing
```{r}
lm_g.frac <- lm(g.frac~Species*scar.BM+Phase+scar.DEN+carn.BM+Phase+Length.cm+PC1+PC2, data=data)
summary(lm_g.frac)
```
*Notes: carn.BM and PC1 are strongest predictors of time spent grazing, scar.BM and phase are also significant. Slight significance of species, length, and species-scar.BM interaction*

@@

### Feeding rates
```{r}
lme_FR <- lme(FR~Phase+Length.cm+Species*scar.BM+scar.DEN+carn.BM+PC1+PC2,data=data,random=~1|Island, na.action = na.omit)
summary(lme_FR)
```
*Notes: nearly everything is significant except for PC2 and scar.DEN?*

### Fraction of time spent grazing
```{r}
lme_g.frac <- lme(g.frac~Phase+Length.cm+Species*scar.BM+scar.DEN+carn.BM+PC1+PC2,data=data,random=~1|Island, na.action = na.omit)
summary(lme_g.frac)
```
*Notes: carn.BM and phase are strongest predictors, followed by scar.BM, PC1, and length. Also significant interaction between *

@@

## GAMMs
```{r, echo=FALSE}
gamm<-gamm(FR~Species+Phase+s(Length.cm)+s(scar.BM)+s(PC1)+s(PC2), family=gaussian(link=identity),data=data, random=list(Island=~1),method="REML")
summary(gamm$gam)
plot(gamm$gam,pages=1)
```
### Modelling effects of predictors

```{r, message=FALSE,warning=FALSE,echo=FALSE}
gamm<-gamm(FR~Species+Phase+s(Length.cm)+s(scar.BM)+s(PC1)+s(PC2), family=gaussian(link=identity),data=data, random=list(Island=~1),method="REML")
summary(gamm$gam)
plot(gamm$gam,pages=1)
```
```{r, message=FALSE,warning=FALSE,echo=FALSE}
gamm1<-gamm(g.frac~Species+Phase+s(Length.cm)+s(scar.BM)+s(PC1)+s(PC2), family=gaussian(link=identity),data=data, random=list(Island=~1),method="REML")
summary(gamm1$gam)
plot(gamm1$gam,pages=1)
```
------------------------

>>>>

## Basic lm
-site-level predictors: scar.BM, scar.DEN, benthic (PC1,PC2)
-fish-level predictors: species, phase, length
--eventually run separately for different species
--species*scar.BM interaction?

```{r}
lm_FR <- lm(FR~scar.BM*Species+Phase+Length.cm+PC1+PC2, data=data)
summary(lm_FR)
```
*Notes: nearly everything is significant? Significant interaction between scar.BM and species for Spar. viride.*
*R2 goes up slightly with initial only*

### Adding spearfishing variable
```{r}
lm_FR <- lm(FR~scar.BM*Species+Phase+Length.cm+PC1+PC2+Spearfishing, data=data)
summary(lm_FR)
```
*Notes: spearfishing masks benthic (PC1/PC2 effects), because highly correlated...*

@@

```{r}
lme_FR <- lme(FR~Phase+Length.cm+Species*scar.BM+PC1+PC2+carn.BM,data=data,random=~1|Island, na.action = na.omit)
summary(lme_FR)
```
*Notes: including island as a random effect makes all site-level variables non-significant. Adding carn.BM back in makes *

### Fraction of time spent grazing
```{r}
lme_g.frac <- lme(g.frac~Phase+Length.cm+Species*scar.BM+scar.DEN+PC1+PC2,data=data,random=~1|Island, na.action = na.omit)
summary(lme_g.frac)
```
*Notes: carn.BM and phase are strongest predictors, followed by scar.BM, PC1, and length. Also significant interaction between Spar. viride and scar.BM*

@@

## GAMMs
```{r, echo=FALSE}
gamm<-gamm(FR~Species+Phase+s(Length.cm)+s(scar.BM)+s(PC1)+s(PC2), family=gaussian(link=identity),data=data, random=list(Island=~1),method="REML")
summary(gamm$gam)
plot(gamm$gam,pages=1)
```
